### 2023-11-14 main.tex
Steady State
''

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\begin{cases}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
	\end{cases}
\end{equation}
with commutaion relations
\begin{equation}
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
\end{equation}
Therefore, we have that 
\begin{equation}
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
\end{equation} 
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
\end{comment}
\section{Exact steady state of $H$}\label{appB}

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$

@@

@@

In \eqref{SteadyState-coeff-implicit} there are two terms. For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}. The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$. If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.

@@

	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
	\end{equation}
thus
\begin{equation}
\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
S_{1}^{-1}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)(1-\delta_{\mu_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)(1-\delta_{\mu_{L},N})|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
\end{equation}
\begin{comment}
	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
	\begin{equation}
		\begin{split}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
			\\&
			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
		\end{split}
	\end{equation}
	where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\begin{equation}
		%\eta_{x}=\begin{cases}
			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
			%	d_{x}\qquad &\text{otherwise}
			%\end{cases}\qquad
			\theta_{x}(b)=\begin{cases}
				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
				N \qquad &\text{otherwise}
			\end{cases}
		\end{equation}
		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
		\begin{align*}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
			\\&\otimes
			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
			\\&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
		\end{align*}
		\begin{comment}

@@

		|\Psi^{'}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{'}(\bm{\mu})|\bm{\mu}\rangle

@@

				\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})

@@

@@

	\textbf{Proof of the normalization}: we aim to show that 

>>>>

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
with commutaion relations
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
Therefore, we have that 
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
\section{Exact steady state of $H$}\label{appB}
\begin{proposition}[Non-equilibrium steady state]
The non-equilibrium steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
	|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
where for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$

@@

		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
where the last expectation is taken with respect to the $\mu^{\text{NESS}}$ of the process $\bm{\sigma}$ and is given in \eqref{exactCorrelations}.
\end{proposition} %Therefore, 
%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{x_{q_{k}}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
%\end{equation} are computed using \eqref{exactCorrelations}. \\ \\

@@

%In \eqref{SteadyState-coeff-implicit} there are two terms. For every configuration $\bm{\tau}$ the first term just gives $\Psi^{'}(\bm{\tau})$ from formula \eqref{ABS}. The second term acts as follows: for every $b\in\{1,\ldots,L\}$, if $\bm{\tau}$ has more then $b$ empty occupations, it changes $b$ of these empty occupations in all possible species from $1$ to $N-1$ and gives contributions $\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})$. If $\bm{\tau}$ has less than $b$ empty occupation we do not see any contribution from this second term.

@@

	\paragraph{Proof of formula \eqref{SteadyState-coeff-implicit}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
	\end{equation}
thus
\begin{equation}
\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)(1-\delta_{\mu,N})|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)
\end{equation}
\begin{comment}
	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
	\begin{equation}
		\begin{split}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
			\\&
			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
		\end{split}
	\end{equation}
	where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\begin{equation}
		%\eta_{x}=\begin{cases}
			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
			%	d_{x}\qquad &\text{otherwise}
			%\end{cases}\qquad
			\theta_{x}(b)=\begin{cases}
				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
				N \qquad &\text{otherwise}
			\end{cases}
		\end{equation}
		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
		\begin{align*}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
			\\&\otimes
			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
			\\&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
		\end{align*}
		\begin{comment}

@@

		|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})|\bm{\sigma}\rangle

@@

	\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_x,i_{x}}\right)\nonumber\\
	=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
	=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
In the last equality we exploited the fact that considering any $\tau_{x}\in \{1,\ldots,N\}$ and $i_{x}\in \{1,\ldots,N-1\}$, and considering a configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$ such that 
		\sigma_{x}=i_{x}\qquad &\text{if}\quad x\in \{q_{1},\ldots,q_{b}\}\\
		\sigma_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
we have that 
	 \Psi^{'}(\bm{\sigma})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
as showed in Section \ref{correlation-section}. 
	%			\Psi(\bm{\tau}) &=\langle\bm{\tau}|S_{1}^{-1}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 
	%			\\&
	%			+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})

@@

	\begin{remark}[Proof of \eqref{SteadyState-coeff-implicit} using the conservation of probability]
		Equation \eqref{SteadyState-coeff-implicit} can be proved also using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
			\Psi(\bm{\tau})=&\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega}\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
			=&\sum_{\bm{\sigma}\in \Omega}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\bm{\sigma}|\Psi\rangle\nonumber\\
			=&\sum_{\bm{\sigma}\in \Omega}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
			%=&\sum_{\bm{\sigma}\in \Omega}\langle \bm{\sigma}|D|\bm{\xi}\rangle\langle \bm{\sigma}|\Psi\rangle
Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, one find \eqref{SteadyState-coeff-implicit}. 
where $\bm{\xi}=(\xi^{0},\xi^{1},\ldots,\xi^{L},\xi^{L+1})$ is a dual configuration given by 
	\xi_{a}^{x}=\delta_{\tau_{x},a}\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in \{1,\ldots,L\}\\
	\xi_{a}^{x}=0\qquad &\forall a\in \{1,\ldots,N\},\;\;x\in {0,L+1}
Since the occupations in the extra-sites $\{0,L+1\}$ we can introduce (arguing similarly to the Section \ref{correlation-section}) $\hat{\bm{\xi}}=(\xi^{1},\ldots,\xi^{L})$ and observe that 
\langle \bm{\sigma}|D|\bm{\xi}\rangle=\langle \bm{\sigma}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\dt
Therefore, using the resolution of identity we have and \eqref{S1-Inverse} we have that 
\Psi(\bm{\tau})=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
	\begin{proposition}[Normalization of $|\Psi\rangle$]

@@

\end{proposition}
	\textbf{Proof}: we aim to show that 
